 

# Simulation

## $latex \phi = (-1, 1)^T$

### Experiments

#### Normality Test

##### D = 0, phi = c(-1,1), data.length = 10 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(0,1)$ distributed.
```{r qqnorm-misq1-0-0-0, echo=FALSE}
source("pre.R")
cache.source("misq1-0-0-0.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 0, phi = c(-1,1), data.length = 100 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(0,1)$ distributed.
```{r qqnorm-misq1-0-0-1, echo=FALSE}
source("pre.R")
cache.source("misq1-0-0-1.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 0, phi = c(-0.5,1,-0.5), data.length = 10 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(0,1)$ distributed.
```{r qqnorm-misq1-0-1-0, echo=FALSE}
source("pre.R")
cache.source("misq1-0-1-0.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 0, phi = c(-0.5,1,-0.5), data.length = 100 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(0,1)$ distributed.
```{r qqnorm-misq1-0-1-1, echo=FALSE}
source("pre.R")
cache.source("misq1-0-1-1.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 1, phi = c(-1,1), data.length = 10 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(1,1)$ distributed.
```{r qqnorm-misq1-1-0-0, echo=FALSE}
source("pre.R")
cache.source("misq1-1-0-0.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 1, phi = c(-1,1), data.length = 100 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(1,1)$ distributed.
```{r qqnorm-misq1-1-0-1, echo=FALSE}
source("pre.R")
cache.source("misq1-1-0-1.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 1, phi = c(-0.5,1,-0.5), data.length = 10 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(1,1)$ distributed.
```{r qqnorm-misq1-1-1-0, echo=FALSE}
source("pre.R")
cache.source("misq1-1-1-0.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 1, phi = c(-0.5,1,-0.5), data.length = 100 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(1,1)$ distributed.
```{r qqnorm-misq1-1-1-1, echo=FALSE}
source("pre.R")
cache.source("misq1-1-1-1.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 10, phi = c(-1,1), data.length = 10 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(10,1)$ distributed.
```{r qqnorm-misq1-10-0-0, echo=FALSE}
source("pre.R")
cache.source("misq1-10-0-0.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 10, phi = c(-1,1), data.length = 100 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(10,1)$ distributed.
```{r qqnorm-misq1-10-0-1, echo=FALSE}
source("pre.R")
cache.source("misq1-10-0-1.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 10, phi = c(-0.5,1,-0.5), data.length = 10 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(10,1)$ distributed.
```{r qqnorm-misq1-10-1-0, echo=FALSE}
source("pre.R")
cache.source("misq1-10-1-0.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 10, phi = c(-0.5,1,-0.5), data.length = 100 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(10,1)$ distributed.
```{r qqnorm-misq1-10-1-1, echo=FALSE}
source("pre.R")
cache.source("misq1-10-1-1.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 100, phi = c(-1,1), data.length = 10 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(100,1)$ distributed.
```{r qqnorm-misq1-100-0-0, echo=FALSE}
source("pre.R")
cache.source("misq1-100-0-0.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 100, phi = c(-1,1), data.length = 100 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(100,1)$ distributed.
```{r qqnorm-misq1-100-0-1, echo=FALSE}
source("pre.R")
cache.source("misq1-100-0-1.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 100, phi = c(-0.5,1,-0.5), data.length = 10 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(100,1)$ distributed.
```{r qqnorm-misq1-100-1-0, echo=FALSE}
source("pre.R")
cache.source("misq1-100-1-0.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```
##### D = 100, phi = c(-0.5,1,-0.5), data.length = 100 

- $latex S_1(t)$ is $latex N(0,1)$ distributed.
- $latex S_2(t)$ is $latex N(100,1)$ distributed.
```{r qqnorm-misq1-100-1-1, echo=FALSE}
source("pre.R")
cache.source("misq1-100-1-1.R")
test.normality(sim.data)
print(paste("mean: ", mean(sim.data)))
print(paste("variance: ", var(sim.data)))
```

