# Simulation1: Normal Distributed Error

## Simulation Environment

- $latex e_i$ is distributed as $Normal(0,1) \forall i \in 1, \cdots, n$
- $latex M_2 = 1$
- $latex M_3 = 0$
- $latex M_4 = 3$

Code:

```{r synthetic_data_normal, cache=TRUE, message=FALSE}
library(sm)
sample_size <- 5000
n <- 100
synthetic_data <- matrix(rnorm(sample_size * n), n, sample_size)
expected_result <- c(M_2 = 1, M_3 = 0, M_4 = 3)
```

## Verify $latex e^Te$

The distribution of $latex e^Te$ is:

```{r e^Te_normal, dependson="synthetic_data_normal",echo=FALSE, message=FALSE}
library(sm)
result <- apply(synthetic_data, 2, function(a) t(a)%*%a)
sm.density(result)
abline(v=n * expected_result["M_2"],col='red')
legend('topright', 'expected value', lty=1, col='red')
```

## Verify $latex ee^Te$

The distribution of $latex \left|| ee^Te \right||$ is:

```{r ee^Te_normal, dependson="synthetic_data_normal",echo=FALSE, message=FALSE}
result <- matrix(NA,n,sample_size)
for(i in 1:sample_size) {
  a <- synthetic_data[,i]
  result[,i] <- a %*% t(a) %*% a  
}
cat("simulation result: \n")
print(apply(result,1,mean))
cat("expected result: \n")
retval <- rep(expected_result['M_3'],n)
names(retval) <- NULL
print(retval)
```

## Verify $latex e^Tee^Te$

```{r e^Tee^Te_normal, dependson="synthetic_data_normal", echo=FALSE, message=FALSE}
result <- rep(NA,sample_size)
for(i in 1:sample_size) {
  a <- synthetic_data[,i]
  result[i] <- t(a) %*% a %*% t(a) %*% a
}
sm.density(result)
abline(v= n * expected_result['M_4'] + n * (n-1) * expected_result['M_2']^2,col='red')
```

# Simulation2: Exponential Distributed Error

## Simulation Environment:

- $latex e_i$ is distributed as $Exponential(1) - 1$
- $latex M_2 = 1$
- $latex M_3 = 2$
- $latex M_4 = 9$

code:

```{r synthetic_data_exp , cache=TRUE, message=FALSE}
library(sm)
sample_size <- 5000
n <- 100
synthetic_data <- matrix(rexp(sample_size * n) - 1, n, sample_size)
expected_result <- c(M_2 = 1, M_3 = 2, M_4 = 9)
```

## Verify $latex e^Te$

The distribution of $latex e^Te$ is:

```{r e^Te_exp, dependson="synthetic_data_exp",echo=FALSE, message=FALSE}
library(sm)
result <- apply(synthetic_data, 2, function(a) t(a)%*%a)
sm.density(result)
abline(v=n * expected_result["M_2"],col='red')
legend('topright', 'expected value', lty=1, col='red')
```

## Verify $latex ee^Te$

The distribution of $latex \left|| ee^Te \right||$ is:

```{r ee^Te_exp, dependson="synthetic_data_exp",echo=FALSE, message=FALSE}
result <- matrix(NA,n,sample_size)
for(i in 1:sample_size) {
  a <- synthetic_data[,i]
  result[,i] <- a %*% t(a) %*% a  
}
cat("simulation result: \n")
print(apply(result,1,mean))
cat("expected result: \n")
retval <- rep(expected_result['M_3'],n)
names(retval) <- NULL
print(retval)
```

## Verify $latex e^Tee^Te$

```{r e^Tee^Te_exp, dependson="synthetic_data_exp", echo=FALSE, message=FALSE}
result <- rep(NA,sample_size)
for(i in 1:sample_size) {
  a <- synthetic_data[,i]
  result[i] <- t(a) %*% a %*% t(a) %*% a
}
sm.density(result)
abline(v= n * expected_result['M_4'] + n * (n-1) * expected_result['M_2']^2,col='red')
```
